\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}

\title{SE 3XA3: Problem Statement\\Mario Level X}

\author{Team 210, Mario Level X
		\\ Ahmad Gharib - ghariba
		\\ Connor Czarnuch - czarnucc
		\\ Edward Liu - liuz150
}

\date{}


\begin{document}

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
2020-01-03 & All Members & Problem statement brainstorm\\
2020-01-04 & All Members & Problem statement creation\\
\bottomrule
\end{tabularx}
\end{table}

\newpage

\maketitle

\newpage
Due to the growth of technology, gaming has become very popular in recent years, with a diverse range of players. Every year, new games are released using latest engines, cutting edge graphics, and a variety of features to attract players. However, a fundamental reason why people enjoy games is because it allows them to connect with other players like themselves. Individuals are able to contribute to the game to make it better and strangers are able to bond by working together towards a common goal, eventually forming a community of like-minded players. Unfortunately, due to the volume of games that are released, many developers are too focused on using the latest technology to improve marketing, that they forget to incorporate such opportunities for players to connect with the game. We hope to inspire future games creators by focusing on the fundamentals of what makes a game great, by setting our own example.
    \bigskip

    A prime stakeholder of this problem are people who play video games, since the quality of games has a major effect on them. Many people rely on games as a way to relax and socialize with others, so a lack of quality in games may have a negative impact on their lives. Another stakeholder would be game companies and developers as their game quality will impact the success of their business. By creating a platform to allow players to create communities, game companies/developers can create a fan base which will help promote their products and increase their sales.
    \bigskip
    
    Our team hopes to set an example by modifying an existing game by adding features for players to have a more personal and unique experience with the game, as well as maintain the core functionalities. With the original ``mario-level-1'', the game functions correctly as expected, however, the level layout of the game is fixed, so there is no room for users to expand on the game. This hinders the ability for players to interact with the game on a personal level, as they cannot contribute to the community. We feel that is not enough for games to only perform correctly. It is important that the player feels as if they are the main contributor to the enjoyment they get from the game. We aim to modularize level generation portion of the game, to allow players to take part in creating custom levels and potentially share it with others. By doing so, we provide the users with an opportunity to form a community around the game and share their unique experiences. Since our main focus is game development, our target platforms are PC’s and potentially gaming consoles.

\end{document}